Drivers of urban land surface temperature: diurnal and nocturnal

### 2018-01-16 report/article.tex

\documentclass[review]{elsarticle}

@@

\journal{Journal of \LaTeX\ Templates}

@@

\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:
\author{Elsevier\fnref{myfootnote}}
\address{Radarweg 29, Amsterdam}
\fntext[myfootnote]{Since 1880.}

%% or include affiliations in footnotes:
\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
\ead[url]{www.elsevier.com}

\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{support@elsevier.com}

\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
\address[mysecondaryaddress]{360 Park Avenue South, New York}

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

\begin{keyword}
\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
\MSC[2010] 00-01\sep  99-00
\end{keyword}

>>>>

\documentclass[]{elsarticle}
%\documentclass[review]{elsarticle}

@@

\journal{Remote Sensing of Environment}

@@

\title{Drivers of urban land surface temperature: diurnal and nocturnal}

%% or include affiliations in footnotes:
\author[1]{T.M. Logan\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead[url]{www.tomlogan.co.nz}
\ead{tomlogan@umich.edu}

\author[2]{B. Zaitchik}
\author[1]{S. Guikema}

\address[1]{Industrial and Operations Engineering, University of Michigan, Ann Arbor, MI}
\address[2]{Earth and Planetary Sciences, Johns Hopkins University, Baltimore, MD}

\begin{abstract}
Understanding the drivers of urban land surface temperature can assist in ameliorating the severity of the urban heat island and risk from heat waves. Of all the natural events, heat waves are among the deadliest and are likely to become longer and more frequent. These changes, coupled with demographic shifts towards urban living, put significant impetus on reducing community exposure to heat waves. An understudied aspect of urban land surface temperature is factors related to nocturnal surface temperature. Nocturnal land surface temperature is important in heat wave mitigation given the urban heat island effect is most apparent during the night and the minimum nocturnal temperature is linked with heat stress and mortality. In this study, we examine the day and night urban land surface temperature (with Landsat) in seven cities across the United States. We test a series of hypotheses regarding the effect of greenspace, water bodies, and impervious surfaces on land surface temperature using advanced statistical methods. The robustness of these results is tested using different cities and satellite imagery and the results of diurnal and nocturnal analysis are compared to determine if the expected relationships hold throughout the day and night. Understanding whether the factors related to high urban temperatures are consistent across US cities is important for climate adaptation planning and capable predictive models suggest the potential for analysing the effect of potential biophysical changes might have on land surface temperature.
\end{abstract}

\begin{keyword}

\end{keyword}
